---
title: "Unit 1 - 3 Review Starter"
author: "Jetoci"
date: "23/02/2023"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sites)
names(sites)
```

Number of rows = `r nrow(sites)`
Number of variables = `r ncol(sites)`

The rows are the names of minerals and different locations. 

### Exercise 2

```{r inspect-other-data-frames}
glimpse(location_descriptions)
glimpse(density)
glimpse(solubility_hardness)
names(location_descriptions)
names(density)
names(solubility_hardness)
```
Number of rows for location_description = `r nrow(location_descriptions)`
Number of variables for location_description= `r ncol(location_descriptions)`

Number of rows for density = `r nrow(density)`
Number of variables for density = `r ncol(density)`

Number of rows for solubility_hardness = `r nrow(solubility_hardness)`
Number of variables for solubility_hardness= `r ncol(solubility_hardness)`

In the location_descriptions dataframe, the rows corresponds to the location of minerals. In the density dataframe, the rows include the identity of the minerals and the density. In the solubility_hardness dataframe, the rows includes the mineral names, solubility, and hardness.

### Exercise 3

```{r join-mineral-properties}
sand_mineral_properties <- sites %>% 
  left_join(density) %>%
  left_join(solubility_hardness)
  
```
The output has 23 rows, and it is the same as sand_minerals. 

### Exercise 4

```{r sand-grains-per-location}
sand_mineral_properties %>% 
  count(location) 
```
```{r slice-bottom-10}
sand_mineral_properties %>% 
  slice(n = 13:23)
```
```{r arrange-by-density}
sand_mineral_properties %>% 
  arrange(desc(density)) %>% 
  slice(13:23)
```
```{r sand-mineral_location-hardness}
sand_mineral_properties %>%
  select(location, hardness) %>%
  slice(19:23)
```
```{r}
sand_mineral_properties %>% 
  arrange(desc(hardness), na.rm= TRUE) %>% 
  slice(1:5)
```



### Exercise 5

```{r distinct-density-values}
sand_mineral_properties %>% 
  distinct(density)
```
```{r count-minerals}
sand_mineral_properties %>% 
  count(minerals)

```

```{r density_1000}
sand_mineral_properties %>% 
  mutate(density_1000 = density/1000) 
  
```


### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 8

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 9

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
